---
title: "Data Appendix for Putin’s Performance Dilemma..."
author: "Alexander Bor & Levente Littvay"
date: "2016.08.17."
output: pdf_document
---

```{r, include = F}

library(ggplot2)
library(stargazer)
library(pander)
std <- function(x) sd(x)/sqrt(length(x))

set.seed(13012)

####   Set working directory

####   The working directory should be set to the "Command files" directory in 
####   which this script is stored.
####   In the command below, replace "<PATH TO `Command files' DIRECTORY>" with the 
####   directory path (for the computer you are working on) to the "Command files" dir.

# setwd("<PATH TO `Command files' DIRECTORY>")
setwd("/Users/szasulja/Dropbox/thesis/Russia paper ProjectTIER/processing-and-analysis/command-files")

###  load dataset

load("../analysis-data/ESS5RU_final.Rdata")

```

All variables in the analysis come from the ESS data. The data consist of `r nrow(data_out)` observations. Definitions, summary statistics, and distributions of all variables are shown below.

\bigbreak
\bigbreak

__Variable:__ TRSTPRL

__Definition:__ Trust in Parliament 

```{r, echo=F}

pander(summary(data_out$TRSTPRL))

hist(data_out$TRSTPRL, 
     xlab = c("Trust in Parliament"), 
     main = NULL)

```

\newpage 

__Variable:__ TRSTLGL

__Definition:__ Trust in Legal system

```{r, echo=F}

pander(summary(data_out$TRSTLGL))

hist(data_out$TRSTLGL, 
     xlab = c("Trust in Legal System"), 
     main = NULL)

```

\newpage 

__Variable:__ TRSTPLC

__Definition:__ Trust in police

```{r, echo=F}

pander(summary(data_out$TRSTPLC))

hist(data_out$TRSTPLC, 
     xlab = c("Trust in police"), 
     main = NULL)

```

\newpage 

__Variable:__ TRSTPLT

__Definition:__ Trust in politicians

```{r, echo=F}

pander(summary(data_out$TRSTPLT))

hist(data_out$TRSTPLT, 
     xlab = c("Trust in politicians"), 
     main = NULL)

```

\newpage 

__Variable:__ TRSTPRT

__Definition:__ Trust in political parties

```{r, echo=F}

pander(summary(data_out$TRSTPRT))

hist(data_out$TRSTPRL, 
     xlab = c("Trust in parties"), 
     main = NULL)

```

\newpage 

__Variable:__ TR

__Definition:__ Trust index of the five institutional trust evaluations as exported from the model

```{r, echo=F}

pander(summary(data_out$TR))

hist(data_out$TR, 
     xlab = c("Trust-index"), 
     main = NULL)

```

\newpage 



__Variable:__ TRSTPPL

__Definition:__ Trust in people in general

```{r, echo=F}

pander(summary(data_out$TRSTPPL))

hist(data_out$TRSTPPL, 
     xlab = c("Trust in people"), 
     main = NULL)

```

\newpage 

__Variable:__ PARTYUR

__Definition:__ Feels close to the United Russia party

```{r, echo=F}

pander(summary(data_out$PARTYUR))

barplot(table(data_out$PARTYUR), 
     xlab = c("Feeling close to UR"), 
     main = NULL)

```

\newpage 

__Variable:__ STFECON

__Definition:__ Level of satisfaction with "the current state of economy" 

```{r, echo=F}

pander(summary(data_out$STFECON))

hist(data_out$STFECON, 
     xlab = c("Satistaction with the economy"), 
     main = NULL)

```

\newpage 

__Variable:__ AGEA

__Definition:__ Age of the respondent 

```{r, echo=F}

pander(summary(data_out$AGEA))

hist(data_out$AGEA, 
     xlab = c("Age"), 
     main = NULL)

```

\newpage

__Variable:__ AGEGEN

__Definition:__ Age categorized by generations (marked by leader's name in childhood)

```{r, echo=F}

pander(summary(data_out$AGEGEN))

barplot(prop.table(table(data_out$AGEGEN)), 
     xlab = c("Age by generations"), 
     main = NULL)

```

\newpage 


\newpage 

__Variable:__ EDUCAT

__Definition:__ Highest level of education achieved.

```{r, echo=F}

pander(summary(data_out$EDUCAT))

barplot(prop.table(table(data_out$EDUCAT)), 
     xlab = c("Highest education completed by respondent"), 
     main = NULL)

```

\newpage 

__Variable:__ POPSIZE

__Definition:__ Population size of place of residence

```{r, echo=F}

pander(summary(data_out$POPSIZE))

barplot(prop.table(table(data_out$POPSIZE)), 
     xlab = c("Population size of place of residence"), 
     main = NULL)

```

\newpage 

__Variable:__ PROTEST

__Definition:__ A dummy capturing if respondent belongs to the category most likely to show up at protests in _all three_ of the demographic variables (Putin's generation, Has higher education, lives in a big city)

```{r, echo=F}

pander(summary(data_out$PROTEST))

barplot(prop.table(table(data_out$PROTEST)), 
     xlab = c("Most likely to protest"), 
     main = NULL)

```

\newpage 

__Variable:__ Male

__Definition:__ Sex of respondent coded as a male-dummy

```{r, echo=F}

pander(summary(data_out$MALE))

barplot(prop.table(table(data_out$MALE)), 
     xlab = c("Proportion of males"), 
     main = NULL)

```

\newpage 

__Variable:__ WORKORG

__Definition:__ Whether the respondent worked in an organisation or association during the past 12 months

```{r, echo=F}

pander(summary(data_out$WORKORG))

barplot(prop.table(table(data_out$WORKORG)), 
     xlab = c("Did any social work?"), 
     main = NULL)

```

\newpage 

__Variable:__ POLINTR

__Definition:__ Interest in politics. Coded as dummy: Very or quite interested

```{r, echo=F}

pander(summary(data_out$POLINTR))

barplot(prop.table(table(data_out$POLINTR)), 
     xlab = c("Interest in politics"), 
     main = NULL)

```

\newpage 

__Variable:__ INTERNET

__Definition:__ How often do you use the internet? Coded as dummy: Several times a week or daily.

```{r, echo=F}

pander(summary(data_out$INTERNET))

barplot(prop.table(table(data_out$INTERNET)), 
     xlab = c("Uses internet at least several times a week"), 
     main = NULL)

```

\newpage 

__Variable:__ VOTED

__Definition:__ Voted in last elections

```{r, echo=F}

pander(summary(data_out$VOTED))

barplot(prop.table(table(data_out$VOTED)), 
     xlab = c("Voted in the last elections"), 
     main = NULL)

```

\newpage 


__Variable:__ C

__Definition:__ Which latent class the respondent belongs to? 

```{r, echo=F}

pander(summary(data_out$C))

barplot(prop.table(table(data_out$C)), 
     xlab = c("Latent class membership"), 
     main = NULL)

```
